% ##########################################################################################################
% Param
% ##########################################################################################################

\documentclass[10pt, a4paper]{moderncv}
\moderncvtheme[blue]{classic}
\usepackage[utf8]{inputenc}
\usepackage[inline]{enumitem}

% Marge aux 4 coins de la page, ici elles sont réduites pour gagner de la place
\usepackage[
  top=1.0cm, bottom=1.0cm,
  left=1.0cm, right=1.0cm
]{geometry}
% Largeur de la colonne de gauche pour les dates
\setlength{\hintscolumnwidth}{2.7cm}

% remove step between item
\usepackage{enumitem}
\setlist{nolistsep,leftmargin=*}

% ##########################################################################################################
% Whoami
% ##########################################################################################################

\firstname{Florian}
\familyname{ccj}
\email{askme.com}
\mobile{+33 (7) 66 66 66 66}
\title{Systems Administrator / Devops Engineer}
\address{Bastille}{75011 Paris}
%\homepage{}

%\extrainfo{}

% ##########################################################################################################
% Content
% ##########################################################################################################

\begin{document}
\maketitle
% Marge négative entre le titre et la partie expérience, pour gagner de la place
\vspace*{-2.5\baselineskip}

% **********************************************************************************************************
% Experience
% **********************************************************************************************************

%\section{Work Experience}

\section{Professional}

\cventry{oct. 2018\\--- today}{System Administrator}{Ministry of the Armed Forces}{Paris}{}{%
  \begin{itemize}%
    \item Providing tools for developers (Gitlab + CI, SonarQube, Artifactory);
    \item Retrieving and locally installing repositories to allow offline work;
    \item Maintenance and supervising the provided tools;
    \item Supporting developers with continuous integration and continuous deployment processes;
    \item Raising awareness and supporting developers throughout the set up of quality and security processes;
    \item Creating a user community around development and quality best practices;
    \item Exploitation of Kubernetes'clusters.
  \end{itemize}
}
\cventry{oct. 2016\\to oct. 2018}{IT Developer}{Ministry of Defense}{Paris}{}{%
  \begin{itemize}%
    \item IT Development using Php/Symfony 2/3;
      \begin{itemize}%
        \item Full stack development using Twig
        \item Interactions with a MySQL database using Doctrine ORM;%
        \item API provision;
        \item Interaction with third-party applications using the API.%
      \end{itemize}%
    \item Development using Angular 2/4.
  \end{itemize}
}
\cventry{2015\\(3 month)}{Internship, log processing job Developer}{Tagattitude (http://en.tagpay.fr)}{Rocquencourt}{}{%
  \begin{itemize}%
    \item Development using Php/MySQL;%
    \item Log browsing in order to raise metrics and statistics.
  \end{itemize}
}
%\cventry{2012\\(1 mois)}{Stage, Développeur Script de reprise de donnée}{(http://www.magelec.com)}{Paris}{}{%
%  \begin{itemize}%
%    \item Développement en Php/MySQL ;
%    \item Extraction de fichiers excel en CSV fournis par le fournisseur pour allimenter la base de donnée des articles mis à disposition sur le site.
%  \end{itemize}
%}

\section{Voluntary Activities}

\cventry{2019 --- Today}{L'Aube d'Ailleurs}{Game Association}{Nantes}{France}{%
  \begin{itemize}
    \item Organisation of a live-action role-playing game, with political background, for around forty participants.
  \end{itemize}
}
\cventry{Sept 2011\\to Sept 2016}{l'Appel de Sussu}{Board game association}{Ivry}{France}{%
  \begin{itemize}
    \item Organisation of event  based on the game universe;
    \item President of the association (2015--1016).
  \end{itemize}
}
\cventry{Sept. 2000\\to Sept. 2017}{EEDF (Scouting)}{}{Paris}{France}{%
  \begin{itemize}
    \item Coaching children from 8 to 15 yo;
    \item All-year project management ending during summer holidays;
    \item Journalism and attending international gathering (Sweden Jamboree 7--8/2011)
  \end{itemize}
}

% **********************************************************************************************************
% Formation
% **********************************************************************************************************

\section{Formations}

\cventry{2011 --- 2016}{ESME Sudria}{Enginneering school}{Ivry-Sur-Seine}{Major in IT, specialisation Emerging Technologies}{%
  \begin{itemize}%
    \item 2nd year of Master project, \textbf{NodeJS}: Speech recognition and autonomous learning in daily management of peripheral devices (2015--2016 7 months)
    \item 1st year of Master project, \textbf{NodeJS}: Synchronisation of two files within the scope of Data Management (2014--2015 4 month)
%    \item \textbf{C++}: Programme générant des deplacements dimultannés et aléatoire de piece d'échequier en respectant les règles du jeu (2015 2 mois) 
  \end{itemize}
}
\cventry{2014 (5 month)}{Shanghai JioTong University}{Enginneering school}{Shanghai}{}{(Embeded System, database, c++ studies)}

% **********************************************************************************************************
% Formation
% **********************************************************************************************************

%\section{Certifications}%

%\cventry{Juillet 2017}{Certification LFCE}{The Linux Foundation}{Valide 2 ans}{\href{https://www.alexis-madrzejewski.com/ressources/lfce-madrzejewski.pdf}{LFCE-1700-0334-0200}}{%
%Certification \textit{Linux Foundation Certified Engineer} créé par \textit{The Linux Foundation}.
%Les compétences testées sont en rapport avec Linux et l'administration système avancé.\newline
%}
%\cventry{Août 2016}{Certification LFCS}{The Linux Foundation}{Valide 2 ans}{\href{https://www.alexis-madrzejewski.com/ressources/lfcs-madrzejewski.pdf}{LFCS-1600-0922-0100}}{%
%Certification \textit{Linux Foundation Certified System Administrator}.
%}

% **********************************************************************************************************
% Competence
% **********************************************************************************************************

\section{Skills} % \section{Compétences en informatique}
\cvitem{\textbf{OS}}{Centos 7, Debian 7/8/9}
\cvitem{\textbf{Prog.}}{CSS, HTML, PHP, SQL, Python3, BASH, JS, Docker}
\cvitem{\textbf{Framework/Lib.}}{Angular 2/4, Symfony 2/3/4, Sphynx, Bootstrap 3}
\cvitem{\textbf{Admin.}}{Ansile, Apache, Nginx, K8S, Artifactory, Vault, SonarQube, MySQL, Git, Gitlab, Gitlab-ci}
%\cvitem{\textbf{Sécurité}}{Notions SELinux, CSF, iptables, firewalld}
\cvlanguage{\textbf{Anglais}}{read, write, speak --- \underline{Technical}: read, write }{Toeic 815 \texttt{/} 990}
\cvdoubleitem{\textbf{Spanish}}{High-School level}{\textbf{Chinese}}{Notions}

% **********************************************************************************************************
% Interests
% **********************************************************************************************************

\section{Hobbies}

\cvdoubleitem{\textbf{Games}}{Board games, Go, Role Playing Game}{\textbf{Reading}}{Mangas, Fantasy, Science Fiction}
\cvitem{\textbf{Art}}{Circus, Cardistry, Magic, Drawing, Sewing, Cooking, Recorder (Flute), Web Design}
\cvitem{\textbf{Science}}{Mathematics, Computer Science}

\end{document}
